Response to referee

### 2024-04-02 paper/resp_referee.qmd
update

---
title: "Response to referee"
format: pdf
editor: visual
---

@@

• Section 1.1. It would perhaps be useful to provide the expression
of the phase angle, $\varphi(\omega)$ in terms of the real and imaginary part of
the transfer function of the linear filter.
• Section 1.1. The symbol p for the period is already in use from the
previous section, where it denotes the bandwidth and number of
past observations used by the filter.
• Page 4. The definition of the high-pass component (oscillations
in the frequency range from $\pi/6$ to $\pi$ as undesirable oscillations is
controversial.
• Figure 1. In the caption, the ration $I/C$ was never defined before.
The description of the three panels should be better explained in
the main text.
• Section 1.2 makes a reference to X-11 and X-13-ARIMA. The author
assumes that the reader is knowledgeable about seasonal adjustment
methods. Perhaps the authors should state that their
intent is to separate the trend-cycle component from the ’noise’
component.
• Page 7, line 38. ’which extends’ is repeated twice.
• Page 8. What is the meaning of $y_1^*n\dots, y_h^*$ being the implicit forecasts
induced by $w_0$, etc.? The forecasts are obtained from an assumed
polynomial trend model?
• Table 1. Some criteria are labelled as Guggemos, not referenced in
the main text.
• Figures 6-7. The labels of the time axes and the months are in
French.

@@

@@

1) The paper lacks in describing the contribution from the beginning. I had to read the paper a couple of times to clearly identify the contribution. I found the contribution of the paper clearly stated on page 16, but I think I should come before in the text.
2) The paper omits to consider the Covid19 period and how this influences the trend
and cycle decomposition. I understand that this is not the main focus of the paper,
but at least the authors should address this problem in word and possible solution
to address it, e.g. outlier correction, robust distributions, etc.
3) I think a quote from other works can be removed from the paper. For example, I
would remove the quote in point 2) of page 7.

>>>>

---
title: "Response to referee"
format: pdf
---

@@

- Section 1.1. It would perhaps be useful to provide the expression
of the phase angle, $\varphi(\omega)$ in terms of the real and imaginary part of
the transfer function of the linear filter.
- Section 1.1. The symbol p for the period is already in use from the
previous section, where it denotes the bandwidth and number of
past observations used by the filter.
- Page 4. The definition of the high-pass component (oscillations
in the frequency range from $\pi/6$ to $\pi$ as undesirable oscillations is
controversial.
- Figure 1. In the caption, the ration $I/C$ was never defined before.
The description of the three panels should be better explained in
the main text.
- Section 1.2 makes a reference to X-11 and X-13-ARIMA. The author
assumes that the reader is knowledgeable about seasonal adjustment
methods. Perhaps the authors should state that their
intent is to separate the trend-cycle component from the ’noise’
component.
- Page 7, line 38. ’which extends’ is repeated twice.
- Page 8. What is the meaning of $y_1^*n\dots, y_h^*$ being the implicit forecasts
induced by $w_0$, etc.? The forecasts are obtained from an assumed
polynomial trend model?
- Table 1. Some criteria are labelled as Guggemos, not referenced in
the main text.
- Figures 6-7. The labels of the time axes and the months are in
French.

@@

Those sections are now numbered

@@

1) The paper lacks in describing the contribution from the beginning. I had to read the paper a couple of times to clearly identify the contribution. I found the contribution of the paper clearly stated on page 16, but I think I should come before in the text.

2) The paper omits to consider the Covid19 period and how this influences the trend
and cycle decomposition. I understand that this is not the main focus of the paper,
but at least the authors should address this problem in word and possible solution
to address it, e.g. outlier correction, robust distributions, etc.

> 3) I think a quote from other works can be removed from the paper. For example, I
would remove the quote in point 2) of page 7.

Removed
